### 2013-03-28 doc/sosp13/tasks.tex
mr

void search(GlobalAddress<node_t> node, key_t key) {
  if (node.key == key) {
    result = node;
    return;
  }

  parallel_for(0, node.numChildren, &index) {
    search(node.children[index], key);
  }

>>>>

void search(GlobalAddress<node_t *> node, key_t key) {
  if (node->key == key) {
    result = node;
    return;
  }

  parallel_for(0, node->numChildren, &index) {
    search(node->children[index], key);
  }
